**Title**: Linking pinyon jay population abundance to pinyon cone production and climate in the SW United States

### 2024-10-07 drafts/draftAug2024.qmd
updated spatial sampler but model takes sooo long

| Covariate or interaction           | Description (all are at 4x4 km grid cell scale)                                                | Question                                                                                                                          |
|------------------|---------------------------|---------------------------|
| Pinyon pine cone abundance         | Abundance of cones from a predictive model (CITE)                                              | How is pinyon jay abundance linked to pinyon cone availability (can have lead, immediate, and lagged effects)?                    |
| Maximum temperature                | A proxy for physiological limits and/or insect resource availability (can have lagged effects) | How is pinyon jay abundance linked to physiological limits and/or insect availability?                                            |
| Cumulative precipitation           | A proxy for insect resource availability (can have lagged effects)                             | How is pinyon jay abundance linked to insect availability?                                                                        |
| Monsoonality                       | The degree to which the site depends on monsoon moisture                                       | How is pinyon jay abundance shaped by broad-scale climatic mediators of cone reliability?                                         |
| Pinyon basal area                  | The basal area of pinyon pine                                                                  | How is pinyon jay abundance shaped by local habitat preferences for food trees?                                                   |
| Cone abundance x Temperature       |                                                                                                | Is the importance of cone abundance for jays mediated by temperature?                                                             |
| Cone abundance x Precipiation      |                                                                                                | Is the importance of cone abundance for jays mediated by precipitation (e.g., more/less availability of insect prey)              |
| Cone abundance x Monsoonality      |                                                                                                | Is the importance of cone abundance for jays different across a range of monsoonal conditions that alter cone reliability?        |
| Cone abundance x Pinyon basal area |                                                                                                | Is the importance of cone abundance for jays different depending on the local habitat configuration and abundance of pinyon pine? |

>>>>

| Covariate or interaction           | Description (all are at 4x4 km grid cell scale)                                                | Question                                                                                                                          |
|------------------------------------|------------------------------------------------------------------------------------------------|-----------------------------------------------------------------------------------------------------------------------------------|
| Pinyon pine cone abundance         | Abundance of cones from a predictive model (CITE)                                              | How is pinyon jay abundance linked to pinyon cone availability (can have lead, immediate, and lagged effects)?                    |
| Maximum temperature                | A proxy for physiological limits and/or insect resource availability (can have lagged effects) | How is pinyon jay abundance linked to physiological limits and/or insect availability?                                            |
| Cumulative precipitation           | A proxy for insect resource availability (can have lagged effects)                             | How is pinyon jay abundance linked to insect availability?                                                                        |
| Monsoonality                       | The degree to which the site depends on monsoon moisture                                       | How is pinyon jay abundance shaped by broad-scale climatic mediators of cone reliability?                                         |
| Pinyon basal area                  | The basal area of pinyon pine                                                                  | How is pinyon jay abundance shaped by local habitat preferences for food trees?                                                   |
| Cone abundance x Temperature       |                                                                                                | Is the importance of cone abundance for jays mediated by temperature?                                                             |
| Cone abundance x Precipiation      |                                                                                                | Is the importance of cone abundance for jays mediated by precipitation (e.g., more/less availability of insect prey)              |
| Cone abundance x Monsoonality      |                                                                                                | Is the importance of cone abundance for jays different across a range of monsoonal conditions that alter cone reliability?        |
| Cone abundance x Pinyon basal area |                                                                                                | Is the importance of cone abundance for jays different depending on the local habitat configuration and abundance of pinyon pine? |
